Summary Outcome Tables

### 2020-07-29 summary_tables_outcomes.Rmd
Set city names from the ithim object

@@

    ft <- flextable(temp1)
    ft <- add_header_row(ft, values = c(' ', 'strike mode'), colwidths = c(3, ncol(temp1) - 3))
    ft <- merge_v(ft, j = 1:3, part = 'body')

@@

>>>>

cities <- names(io)[!names(io) %in% 'scen_prop']

@@

    ft <- flextable(temp1)
    ft <- add_header_row(ft, values = c(' ', 'strike mode'), colwidths = c(3, ncol(temp1) - 3))
    ft <- merge_v(ft, j = 1:3, part = 'body')
    #fix_border_issues(ft)

@@

### Who hit whom matrix for all case cities as CSV {#whw_all_csv}
